### 2018-08-27 evaluation.tex
Revision from Prof. Xue before final submission

>>>>

In Figures~\ref{fig:drawback} and \ref{fig:benefit},
the performance drops slightly as the matrix size increases 
when $NT \ge 16$. Let us explain
the reason behind. There is a synchronization point
at the end of each iteration
of the loop at layer 2 (Figure~2).
This synchronization is an all-to-all 
communication, whose overhead is proportional to $NT^2$.
This overhead is small when $NT$ is 4 or 8 but
increases quickly as $NT$ increases. In addition, the
performance also drops when matrix sizes are 
multiples of 1024, as
GEMM suffers from more memory contention at these matrix
sizes. 
To understand this better,
we have profiled the GEMM execution
for the matrix sizes 3968 and 4096 under $NT_C=4$ and $NC=4$.
The measured bandwidth for packing A (B) are
1.44 (0.89) GB/s for the
matrix size 3968 but drops significantly to 
0.81 (0.44) GB/s for the matrix size 4096. 
As the memory banks in the Phytium 2000+ processor 
are accessed in a non-balanced manner,
the tiling factors $M_c$, $N_c$ and $K_c$ selected
make it more likely for GEMM to suffer from  
memory contention at matrix sizes that are multiples of 1024.

%In GEMM implementation, different matrix layouts (row-major/column-major)
%are first canonicalized to an implementation defined form
%by optionally swapping the $A$ and $B$ operands in $C=\alpha A B+\beta C$.
%And matrix orientation information (transposed vs. non-transposed)
%is eliminated by means of data packing.
%SCP, which works after these transformations, 
%does not rely on specific matrix layouts or orientations.

### 2018-08-27 intro.tex
Revision from Prof. Xue before final submission

To the best of our knowledge, SCP represents
the first work addressing
the inter-thread cache conflicts problem on
architectures with shared non-LRU caches.

>>>>

To the best of our knowledge, SCP represents
the first work addressing
the inter-thread cache conflicts problem for GEMM on
architectures with shared non-LRU caches.
As other level-3 routines, such as TRSM, TRMM, SYMM and HEMM,
call GEMM internally, they should also benefit from SCP,
i.e., the SCP methodology can apply transparently to these
BLAS-3 routines as well.
